ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
Add note about release
Describe get_dataframe

@@

\todo[inline]{Need to archive version of PyKED and cite}

>>>>

The \python|ChemKED| class has one instance method defined, called
\python|get_dataframe|. Using this method, the user can get an instance of a
Pandas~\autocite{pandas} \python|DataFrame| that contains the information in the
list of \python|DataPoint|s. The user can specify the columns provided in the
\python|DataFrame| by passing a list of column names to the
\python|output_columns| argument of the \python|get_dataframe| function. The
possible columns are not case-sensitive and are:

\noindent\begin{itemize*}
    \item \python|'Temperature'|
    \item \python|'Pressure'|
    \item \python|'Ignition Delay'|
    \item \python|'Composition'|
    \item \python|'Equivalence Ratio'|
    \item \python|'Reference'|
    \item \python|'Apparatus'|
    \item \python|'Experiment Type'|
    \item \python|'File Author'|
    \item \python|'File Version'|
    \item \python|'ChemKED Version'|
\end{itemize*}

In addition, specific fields from the Reference and Apparatus attributes can
be included by specifying the name after a colon. These options are:

\noindent\begin{itemize*}
    \item \python|'Reference:Volume'|
    \item \python|'Reference:Journal'|
    \item \python|'Reference:DOI'|
    \item \python|'Reference:Authors'|
    \item \python|'Reference:Detail'|
    \item \python|'Reference:Year'|
    \item \python|'Reference:Pages'|
    \item \python|'Apparatus:Kind'|
\end{itemize*}

% This weirdness is necessary to prevent the list from running over the margin
\noindent\begin{itemize*}
    \item \python|'Apparatus:Facility'|
    \item \python|'Apparatus:Institution'|
\end{itemize*}

Only the first author is printed when \python|Reference| or
\python|Reference:Authors| is selected because the whole author list may be
quite long.

@@

\todo[inline]{Need to archive version of PyKED and cite}
\todo[inline, author=Bryan]{Should we do this even without officially releasing a version?}
